---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# endemic.channels

<!-- badges: start -->
<!-- badges: end -->

The goal of endemic.channels is to provide functions to compute - using geometrical and arithmetic means - and plot endemic channels, using the methodology described in 'Establishing endemic levels of ranges with computer spreadsheets' (Bortman, 1999) as a basis.

## Installation

You can install the development version of endemic.channels like so:

``` r
library(devtools)
devtools::install_github("denisecammarota/endemic.channels")
```

## Example

Calculating the endemic channels for dummy data, called dengueSP, which contains the data on dengue cases in the Sao Paulo municipality in 2010-2023:

```{r example}
library(tidyverse)
library(ggplot2)
library(endemic.channels)
data("dengueSP")
res <- endemic_channel(dengueSP, type = 'geometric', remove_53 = TRUE, show_plot = FALSE)
end_channels <- res[1]
plot <- res[2]
```

The output plot should look something like this:

```{r plot}
print(plot)
```


